Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-16 Ben_Manuscripts/structure_paper/supporting_information.tex
spellchecking.

\externaldocument[M-]{draft}

\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
  cells we studied. We tested systems with semiisotropic and anisotropic pressure 
  coupling since the shape of the unit cell will likely need to change in order to 
  accomodate hexagonally packed pores.

  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
  observe any progress towards system ordering. In both cases, we see that the nematic
  order parameter stays close to zero for the duration of the simulation time, indicating
  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
  are slightly negative since there are only 400 monomers. 
  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
  proper choice of nematic director, measured values will range between 0 and 1. With a 
  large number of samples, an isotropic system would have an order parameter of 0.

@@

  \vspace{1em}
  We parameterized monomers according to the following procedure:
  \begin{enumerate}
	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch
	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
	explicitly. We optimized the 3D geometry of the structure using the 'Clean in
	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
	converted it to .pdb format using Open Babel 2.4.1
	\cite{oboyle_open_2011,noauthor_open_nodate}. 
	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
	the .pdb structure file as input, we ran
	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
	The net charge on the monomer is input as -1 since the sodium ion is kept as 
	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools16_2016} and the
	output of \texttt{antechamber} to create Amber topology files. A detailed
	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
	\item \textit{Create GROMACS topologies from Amber output} : The output
	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
	\texttt{LEaP} output into GROMACS .gro and .top files. 
	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the box with edges of the
	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimzation
	on the system with the steepest descent algorithm. Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory. 
	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
	configuration taken from the annealed trajectory, we reassigned charges using
	\texttt{molcharge} with the am1bccsym method in order to ensure charges 
	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
	The charges in the GROMACS topology file (.top) were replaced with the 
	new charges calculated by \texttt{molcharge}. 
	\item \textit{Anneal again to get final structure} : We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10 \% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).
  \end{enumerate}

@@

  We may be able to simulate systems using less than 20 monomers per column, but chose
  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
  patterns. The size of the fourier space bin in each dimension is determined by 
  $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
  the resolution would increase the noise in the simulated patterns and make it more
  difficult to measure the intensity of reflections of interest.

@@

		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
		have a test system with an intial spacing below the experimental value. As soon
		as the restraining potential switches to 56 KJ mol$^{-1}$ nm$^{-2}$, the
		columns are able to repel resulting in a large jump in pore spacing
		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
%		There is a large uncertainty in this value because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
%                towards cubic packing.

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~and the initial distance between layers
	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
	  as the average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the timeseries
	  representing the average pore radius at each frame. We detected equilibration
	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
	  and standard deviation of pore radii using only data points collected after
	  equilibration was detected.

@@

		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
		slightly larger than the equilibrated pore radius of the system simulated with
		an intial pore radius of 2.5 \AA. After being run through the full dry
		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
		agrees with the 2.5 \AA~configuration within uncertainty.

@@

	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
	  with an initial layer spacing of 10 \AA~immediately after the restrained
	  portion of the equilibration procedure. Since we used position restraints, the
	  simulations were run in the NVT ensemble. When layer spacing is large, such as
	  this situation, there is a significant amount of vacuum space which the monomer
	  attempts to fill. Even if turning pressure control on allows the system to
	  recover the geometry of the hexagonal phase, we would likely need much longer
	  equilibration times, and it will almost certainly get trapped in a metastable
	  configuration that bears no resemblence to the experimental profile.

	  \begin{figure}[!htb]
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{When layers are initially stacked 10 \AA~apart and the system
                is equilibrated using the dry equlibration procedure, large vacuum gaps
		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
	  \end{figure}

@@

  We developed equilibration schemes to create dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. To create a dry configuration, we fix monomer head groups in the
  sandwiched or parallel-displaced configuration using position restraints with a
  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
  the NVT ensemble which allows the monomer tails to settle without disrupting
  the ordering of the head groups. Doing so also mitigates system dependence on
  initial monomer configuration. Every 50 ps, we reduce the force constants by
  the square root of its previous value. Once the force constant is below 10 KJ
  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
  with pressure controlled by the berendsen barostat. Next, we run long NPT
  equilibration simulations for at least 400 ns using the Parrinello-Rahman
  barostat with a time constant of 10 ps.

@@

  We measured R-spots by calculating the average intensity within a region 
  selected by visual inspection. We report the average intensity within the regions 
  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernable
  spots, we report the average intensity at the intersection of R-alkanes with
  the $q_z$ value of R-double since that is where we expect it to appear based on
  experiment. Since R-double does not appear in our simulated patterns, we 
  estimate where it should appear as half of the $q_z$ value of R-$\pi$.

@@

  The magnitude of noise in the simulated diffraction patterns decrease as 
  the number of independent configurations increases. We simulated the structure
  factor of 100 randomly placed particles and varied the number of independent 
  configurations (N). It is expected that the structure factor should resemble
  a two-dimsional gaussian. We cannot sample enough independent configurations
  of our system to completely eliminate noise.

@@

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit paramaters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on lorentzian parameters
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{(a) We estimated the system's experimental correlation length using a 
  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a lorentzian curve 
  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
  The correlation length is 1/FWHM.}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disorderd Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \hspace{-1cm}
%                \vspace{1cm}
%                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
%                \caption{}\label{fig:tails_topview}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{tails_rzplot.png}
%                \caption{}\label{fig:tails_rzplot}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=0.5\textwidth]{centroids_box.png}
		\caption{Monomer tails pack together hexagonally. The centroid
			of each tail is visualized as a blue sphere. The centroids are calculated based
			on the red atoms in Figure~\ref{fig:monomer_color_coded}. The red sphere
			highlights an example of an alkane tail centroid with its nearest neighbors
			(green spheres) surrounding it in a hexagonal pattern.}\label{fig:centroids}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{angles_traj_layered.png}
%                \caption{}\label{fig:angle_distribution}
%        \end{subfigure}
%        \caption{(a) The trajectory can be stripped of all atoms except carbon
%        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
%        still gives rise to R-spots. (c) Finding the center of mass and visualizing
%        their coordinates reveals the hexagonal-like packing of the tails. (d) The
%        distribution created by measuring the angle between each centroid (e.g. red
%        in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
%        plane has distinct spikes near 30\degree, which is consistent with the location
%        of R-spots}\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{water_filled_pore.png}
                \caption{}\label{fig:water_filled_pores}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{water_removed.png}
                \caption{}\label{fig:water_removed}
        \end{subfigure}
  \caption{(a) Pores built in the parallel displaced configuration with 5
	  monomers per layer are filled with 5 wt\% water. (b) The same system is
	  visualized with water molecules and sodium ions removed. Head groups vacate the
	  pore region leaving an aqeuous solution of water and sodium ions.}\label{fig:water_pores}
  \end{figure}

  \section{Demonstrative fourier transforms}\label{section:fourier}

@@

  \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the nernst-einstein relation yield
        agreeing values of ionic conductivity for both types of ordered basin systems 
        simulated. Both methods estimate the value of the ionic conductivity to be an 
        order of magnitude higher than the experimental value. There is more noise in
        the collective diffusion model because there is inherently less data that 
        can be used for its calculation. For that reason, we use only the Nernst 
        Einstein relationship in the main text.}
        \label{fig:conductivity}
  \end{figure}

@@

>>>>

\externaldocument[M-]{draft}
%MRS8: can use document class here - looks weird with title/authors as written.
\title{Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

@@

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
  coupling since the shape of the unit cell will likely need to change in order to 
  accommodate hexagonally packed pores.

  We use the nematic order parameter as defined in section~\ref{method:nematic_order} to 
  observe any progress towards system ordering. In both cases, we see that the nematic
  order parameter stays close to zero for the duration of the simulation time, indicating
  an isotropic arrangement of head groups (Figure~\ref{fig:nematic_isotropic}). The values
  are slightly negative since there are only 400 monomers. 
  Equation~\ref{eqn:nematic_order_parameter} is bounded between -1 and 1, however, with a
  proper choice of nematic director, measured values will range between 0 and 1. With a 
  large number of samples, an isotropic system would have an order parameter of 0.

@@

  \vspace{1em}
  We parameterized monomers according to the following procedure:
  \begin{enumerate}
	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch
	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
	explicitly. We optimized the 3D geometry of the structure using the 'Clean in
	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
	converted it to .pdb format using Open Babel 2.4.1
	\cite{oboyle_open_2011,noauthor_open_nodate}. 
	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
	the .pdb structure file as input, we ran
	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
	The net charge on the monomer is input as -1 since the sodium ion is kept as 
	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools16_2016} and the
	output of \texttt{antechamber} to create Amber topology files. A detailed
	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.
	\item \textit{Create GROMACS topologies from Amber output} : The output
	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
	\texttt{LEaP} output into GROMACS .gro and .top files. 
	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the box with edges of the
	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimization
	on the system with the steepest descent algorithm. Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory. 
	\item \textit{Reassign charges with \texttt{molcharge}}: With the monomer
	configuration taken from the annealed trajectory, we reassigned charges using
	\texttt{molcharge} with the am1bccsym method in order to ensure charges 
	are symmetric. This condition is not guaranteed with \texttt{antechamber}. 
	The charges in the GROMACS topology file (.top) were replaced with the 
	new charges calculated by \texttt{molcharge}. 
	\item \textit{Anneal again to get final structure} : We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10 \% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).
  \end{enumerate}

@@

  We may be able to simulate systems using less than 20 monomers per column, but chose
  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
  patterns. The size of the Fourier space bin in each dimension is determined by 
  $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
  the resolution would increase the noise in the simulated patterns and make it more
  difficult to measure the intensity of reflections of interest.

@@

		\item 39 \AA~: We tested a pore spacing of 39 \AA~in order to
		have a test system with an initial spacing below the experimental value. As soon
		as the restraining potential switches to 56 kJ mol$^{-1}$ nm$^{-2}$, the
		columns are able to repel resulting in a large jump in pore spacing
		(Figure~\ref{fig:p2p_39}). %After 400 ns, the pore spacing is 4.05 $\pm$ 0.17 nm.
%		There is a large uncertainty in this value because the 1-4 pore spacing
%		(Figure~\ref{fig:p2p_diagram}) deviates significantly from all other pore
%		spacings. The 1-4 pore spacing is 4.31 nm while the average of all other pore
%		spacings is 3.96 nm. The system deviates from hexagonal geometry and is trending
%                towards cubic packing.

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We recommend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

	  We tested 3 different pore radii, defined as shown in
	  Figure~\ref{fig:pore_radius_illustration}. For each system, we held the initial
	  pore spacing constant at 45 \AA~and the initial distance between layers
	  constant at 3.7 \AA. Equilibrated values of pore radii are presented in
	  Table~\ref{table:radii}. The pore radius in each simulation frame is calculated
	  as the average distance of all carbonyl carbons (See
	  Figure~\ref{fig:pore_radius_illustration}) from their associated pore center.
	  Statistics for the pore radii reported were generated from the time series
	  representing the average pore radius at each frame. We detected equilibration
	  using \texttt{pymbar.timeseries.detectEquilibration}. We calculated the average
	  and standard deviation of pore radii using only data points collected after
	  equilibration was detected.

@@

		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
		slightly larger than the equilibrated pore radius of the system simulated with
		an initial pore radius of 2.5 \AA. After being run through the full dry
		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
		agrees with the 2.5 \AA~configuration within uncertainty.

@@

	  Figure~\ref{fig:dbwl_10} shows the structure of an assembly built
	  with an initial layer spacing of 10 \AA~immediately after the restrained
	  portion of the equilibration procedure. Since we used position restraints, the
	  simulations were run in the NVT ensemble. When layer spacing is large, such as
	  this situation, there is a significant amount of vacuum space which the monomer
	  attempts to fill. Even if turning pressure control on allows the system to
	  recover the geometry of the hexagonal phase, we would likely need much longer
	  equilibration times, and it will almost certainly get trapped in a metastable
	  configuration that bears no resemblance to the experimental profile.

	  \begin{figure}[!htb]
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{When layers are initially stacked 10 \AA~apart and the system
                is equilibrated using the dry equilibration procedure, large vacuum gaps
		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
	  \end{figure}

@@

  We developed equilibration schemes to create dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. To create a dry configuration, we fix monomer head groups in the
  sandwiched or parallel-displaced configuration using position restraints with a
  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
  the NVT ensemble which allows the monomer tails to settle without disrupting
  the ordering of the head groups. Doing so also mitigates system dependence on
  initial monomer configuration. Every 50 ps, we reduce the force constants by
  the square root of its previous value. Once the force constant is below 10 KJ
  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
  with pressure controlled by the Berendsen barostat. Next, we run long NPT
  equilibration simulations for at least 400 ns using the Parrinello-Rahman
  barostat with a time constant of 10 ps.

@@

  We measured R-spots by calculating the average intensity within a region 
  selected by visual inspection. We report the average intensity within the regions 
  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernible
  spots, we report the average intensity at the intersection of R-alkanes with
  the $q_z$ value of R-double since that is where we expect it to appear based on
  experiment. Since R-double does not appear in our simulated patterns, we 
  estimate where it should appear as half of the $q_z$ value of R-$\pi$.

@@

  The magnitude of noise in the simulated diffraction patterns decrease as 
  the number of independent configurations increases. We simulated the structure
  factor of 100 randomly placed particles and varied the number of independent 
  configurations (N). It is expected that the structure factor should resemble
  a two-dimensional Gaussian. We cannot sample enough independent configurations
  of our system to completely eliminate noise.

@@

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a Lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit parameters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on Lorentzian parameters
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{(a) We estimated the system's experimental correlation length using a 
  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a Lorentzian curve 
  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
  The correlation length is 1/FWHM.}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disordered Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \hspace{-1cm}
%                \vspace{1cm}
%                \includegraphics[width=\textwidth,scale=2]{tails_topview.png}
%                \caption{}\label{fig:tails_topview}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{tails_rzplot.png}
%                \caption{}\label{fig:tails_rzplot}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=0.5\textwidth]{centroids_box.png}
		\caption{Monomer tails pack together hexagonally. The centroid
			of each tail is visualized as a blue sphere. The centroids are calculated based
			on the red atoms in Figure~\ref{fig:monomer_color_coded}. The red sphere
			highlights an example of an alkane tail centroid with its nearest neighbors
			(green spheres) surrounding it in a hexagonal pattern.}\label{fig:centroids}
%        \end{subfigure}
%        \begin{subfigure}{0.45\textwidth}
%                \centering
%                \includegraphics[width=\textwidth]{angles_traj_layered.png}
%                \caption{}\label{fig:angle_distribution}
%        \end{subfigure}
%        \caption{(a) The trajectory can be stripped of all atoms except carbon
%        atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
%        still gives rise to R-spots. (c) Finding the center of mass and visualizing
%        their coordinates reveals the hexagonal-like packing of the tails. (d) The
%        distribution created by measuring the angle between each centroid (e.g. red
%        in (c)) and its nearest neighbors (e.g. green in (c)) with respect to the xy
%        plane has distinct spikes near 30\degree, which is consistent with the location
%        of R-spots}\label{fig:tail_packing}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{water_filled_pore.png}
                \caption{}\label{fig:water_filled_pores}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \includegraphics[width=\textwidth]{water_removed.png}
                \caption{}\label{fig:water_removed}
        \end{subfigure}
  \caption{(a) Pores built in the parallel displaced configuration with 5
	  monomers per layer are filled with 5 wt\% water. (b) The same system is
	  visualized with water molecules and sodium ions removed. Head groups vacate the
	  pore region leaving an aqueous solution of water and sodium ions.}\label{fig:water_pores}
  \end{figure}

  \section{Demonstrative Fourier transforms}\label{section:fourier}

@@

  \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the Nernst-Einstein relation yield
        agreeing values of ionic conductivity for both types of ordered basin systems 
        simulated. Both methods estimate the value of the ionic conductivity to be an 
        order of magnitude higher than the experimental value. There is more noise in
        the collective diffusion model because there is inherently less data that 
        can be used for its calculation. For that reason, we use only the Nernst 
        Einstein relationship in the main text.}
        \label{fig:conductivity}
  \end{figure}

@@

% LocalWords:  Na GA Packmol pdb filetype MarvinSketch noauthor nodate GROMACS
% LocalWords:  atomtypes antechamber inpcrd prmtop acpype py silva gro gmx NVT
% LocalWords:  editconf molcharge bccsym cyan png dihedrals pore's ca pt xy kJ
% LocalWords:  kinetically metastable outlier BJC Berendsen barostat Parrinello
% LocalWords:  Rahman solvated solvate Eq XRD alkanes WAXS exp FWHM mon alkane
% LocalWords:  transitioning topview rzplot traj binned wt LLC Subharmonics UV
% LocalWords:  realspace Crosslinking polymerization FRP crosslinking FRPs rb
% LocalWords:  racemic Nernst carboxylate antiparallel llc
